%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------


    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        %\item {Extensive experience in ultrasound imaging, seismic imaging, signal and image processing, structural health monitoring, and non-destructive evaluation.}
        %\item {\summarystyleze{Extensive experience in ultrasound imaging, seismic imaging, signal and image processing, structural health monitoring, and non-destructive evaluation.}}
        \sumitem {Extensive experience in non-destructive evaluation, structural health monitoring, ultrasound imaging, seismic imaging, signal processing, and image processing.}
        \sumitem {Strong background in mathematics, mechanics, wave propagation, and finite difference.}
        \sumitem {Broad and hands-on experience in machine learning, array imaging system design, image segmentation.}
        \sumitem {Excels in project management: actively involved in 6 research projects (over \textdollar 3 MM), prepared 20 reports, made 50 formal presentations, and prepared 8 proposals (3 awarded, \textdollar 560k).}        
         \sumitem {R \& D experience in developing imaging algorithms, such as beamforming, least-squares reverse time migration, TR-MUSIC, DORT, advanced filtering, and wavefield analysis.} 
       
      \end{cvitems}
    }

, deep learning, computer vision, 

 \item {Developed \textbf{reverse-time migration (RTM)} and \textbf{DORT} imaging techniques for damage imaging in a C-17 composite aileron for the first time.}
       \item {Developed a non-contact system with a limited number of data acquisition points using a laser Doppler vibrometer.}

       \item {Wrote four journal papers and three conference papers from this project.}

%---------------------------------------------------------



%%%%%%%%%%%%%%%

  \cvskill
    {Sensor networks} % Category
    {, wind and solar powered accelerometers and strain gauges,} % Skills
   \cvskill
    {Non-contact monitoring} % Category
    {, air-coupled transducers} % Skills
   \cvskill
    {Health Monitoring} % Category
    {Condition-based monitoring for civil infrastructures, plantar pressure monitoring} % Skills
     




\end{cventries}


chemical vapor deposition,scannning electron microscope

	\nocite{he2015damage}
	\nocite{he2016lamb}
	\nocite{he2016lamb2DNZLCC}
	\nocite{he2016quantitative}
	\nocite{he2017Radon}
	\nocite{he2017Least}
	\nocite{leser2017Guided}
	\nocite{he2017Multi}
	\nocite{he2017Ultrasonic}
	\printbibliography[
	heading=none, 
	sorting=ydnt
	]
	
	    %\nocite{Khan2014Prototyping}
    \nocite{Conf_he2016Enhanced}
    \nocite{Conf_cao2010simulation2}
    \nocite{Conf_he2017bvid}
    \nocite{Conf_he2016Rapid}	
    \nocite{Conf_he2013damage}
	\printbibliography[
	heading=none, 
	sorting=ydnt
	]
	
	
	    %\nocite{Khan2014Prototyping}
    \nocite{yuan2013portable}
    \nocite{yuan2015integrated}
    \nocite{yuan2015guided}
    \nocite{he2016portable}
    
	\printbibliography[
	heading=none, 
	sorting=ydnt
	]
	
	\cvsubsection{Conference Proceedings (5)}

\begin{refsection}

\end{refsection}


%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
\cvsubsection{Invention disclosure (4)}

\begin{refsection}

\end{refsection}
	
	


    \cvcoursev
    {}
    {}
    {}
Mechanics of Materials
Principal of Structural Vibration (2)

    {Medical Instrument}

    {Statistics (2)}
    {Partial Differential Equations (2)}

        {Design of Electromechanical Systems}
        {Mechanics and Engineering}


    